---
title: "README"
format: gfm
execute: 
  eval: false
  df-print: paged
---

## Recording Data

Save contract data in a single CSV file within the project directory. The file "[my_records.csv](my_records.csv)" is included as an example:

```{r}
#| eval: true
#| message: false
readr::read_csv("my_records.csv")
```

Each contract, each missed day, and each covered day should be listed on its own row. The `action` column should include a single word for each row: "mentored" or "covered" or "missed". Include the contract price and `date_end` for mentoring. Do not include price or `date_end` for days covered or missed. The `date` column refers to the **kick-off date** when mentoring *or* to the date missed or covered.

## Adding details for each invoice date

The `expand_invoices()` function adjusts a simple CSV file to aid with invoicing at the final Friday of each period—either every two weeks, or each month. It produces a data frame in the following format:

```{r}
#| eval: true
#| message: false
source("invoice_functions.R")
readr::read_csv("my_records.csv") |> 
  expand_invoices()
```

A data frame in this format can then be passed along to `set_table()` for rendering with gt. 

## Rendering Invoices

Invoices can be created either by modifying the Quarto file directly or by using a dedicated function.

### Render the Quarto file in the IDE

Use `hybrid_invoice.qmd` as a template. After setting the document's `date` in the metadata and `date_range` in the parameters in the YAML, use the "Render" button in RStudio or Positron the file to create a PDF.

When rendering the "[hybrid_invoice.qmd](hybrid_invoice.qmd)" file as included, the resulting file is "[hybrid_invoice.pdf](hybrid_invoice.pdf)."

### Render using `render_invoice()`

`render_invoice()` can be used to set details for an invoice and create a PDF without needing to touch a file.

#### Invoice for the period ending on or before today:
```{r}
render_invoice("my_records.csv")
```

The above code, rendered on May 6, produces "[invoice_2025-05-06.pdf](invoice_2025-05-06.pdf)."

#### Set a file name

```{r}
render_invoice("my_records.csv", pdf = "sherman_invoice2.pdf")
```

By default, invoice filenames include the invoice date. Setting the `pdf` argument overrides this default, and the above code produces "[sherman_invoice2.pdf](sherman_invoice2.pdf)."

#### Invoice with an explicit invoice date
```{r}
render_invoice("my_records.csv", invoice_date = "2025-06-18")
```

Setting an explicit invoice date can be handy when preparing invoices ahead of time. This code produces "[invoice_2025-06-18.pdf](invoice_2025-06-18.pdf)."

#### Invoice for the period ending on or before a specific date:
```{r}
render_invoice("my_records.csv", period_date = "2025-04-18", pdf = "sherman_invoice3.pdf")
```

Explicitly choose the date of an invoice period to create a PDF dated today of a *past* invoice that has not yet been resolved. This produces "[sherman_invoice3.pdf](sherman_invoice3.pdf)."

This method can also be used to set a broader range than might usually be chosen, which will adjust the "amount" column:

1. One value in `period_date` will prepare an invoice for the period ending on that day or before.
2. Two values will construct a range and prepare an invoice for all periods ending within the range.
3. More than two values will match each value.

```{r}
render_invoice(
  "my_records.csv", 
  period_date = c("2025-03-01", "2025-06-18"), 
  invoice_date = "2025-06-18")
```

Columns update to reflect the weeks, dates, number of units, and amount due, as shown in "[invoice_2025-06-18.pdf](invoice_2025-06-18.pdf)." 

## Credit

Typst invoice template adapted from Eric Scott's design. Quarto extension adapted from [Jonathan Pedroza's code](https://github.com/jpedroza1228/quarto_extensions/tree/main/invoice).